### 2012-11-04 poster/poster.tex
Small edits to poster

Clojure represents Java's \emph{null} as the value \lstinline{nil},
which has the singleton type \colorbox{yellow}{\lstinline|nil|} in Typed Clojure.
This means, unlike Java's static type system, \emph{null} and reference types are separated as static types.
The programmer can then annotate Java methods and fields, specifying where \emph{null} is allowed.

@@

Some common idioms that Typed Clojure types can express
are usages of Clojure's sequence abstraction, a set of functions providing a common
interface to collections.
These functions include:

\begin{itemize}
\item \lstinline|seq|, which takes a collection (or \lstinline|nil|) and returns
   \begin{itemize}
      \item a true value if the argument is non-empty
      \item a false value if the argument is empty (or \lstinline|nil|)
   \end{itemize}
\item \lstinline|first|, which takes a collection (or \lstinline|nil|) and returns
   \begin{itemize}
      \item the first item of the argument if the argument is non-empty
      \item \lstinline|nil| if the argument is empty (or \lstinline|nil|)
    \end{itemize}
\end{itemize}

@@

Heterogeneous map types that record the \emph{presence} of keyword keys
are sufficient to type check the most common Clojure idiom of using plain maps with known keyword keys.

\begin{description}
  \item[Map Literals] \colorbox{codebg}{\lstinline|\{:a 1 :b 2\}|} creates a map value with two entries, and
        is of the heterogeneous map type \colorbox{yellow}{\lstinline{'\{:a Number :b Number\}}}
  \item[Associating keyword keys] \colorbox{codebg}{\lstinline|(assoc \{:a 1 :b 2\} :c 3)|} 
    associates entry with key \lstinline|:c|, and
        is of type \colorbox{yellow}{\lstinline{'\{:a Number :b Number :c Number\}}}
  \item[Dissociating keyword keys] \lstinline|(dissoc {:a 1 :b 2} :a)| dissociates entry with key \lstinline|:a|, and
        is of type \colorbox{yellow}{\lstinline|'\{:b Number\}|}
  \item[Keyword lookup] \lstinline|(get {:a 1 :b 2} :a)| returns the value corresponding to the key \lstinline|:a|, and
        is of type \colorbox{yellow}{\lstinline|Number|}
\end{description}

@@

A function relying heavily on Java interoperability was ported successfully.
This function chained several Java calls together, and
Typed Clojure was able to express and check invariants, mostly related to occurrences of \emph{null}
and primitive arrays.

@@

There is significant future work, including:

@@

\begin{posterbox}[name=references,column=2,below=conclusion]{References}
  \smaller
  \bibliographystyle{ieee}
  \renewcommand{\section}[2]{\vskip 0.05em}
  \begin{thebibliography}{1}\itemsep=-0.01em
    \setlength{\baselineskip}{0.4em}
    \bibitem{tob10:bnb}
    Tobin-Hochstadt, S.
    \newblock {T}yped {S}cheme: {F}rom {S}cripts to {P}rograms (2010)
    \newblock PhD Dissertation,
    \newblock Northeastern University
  \end{thebibliography}
  \vspace{0.3em}

>>>>

Clojure represents Java's \emph{null} as the value \colorbox{codebg}{\lstinline{nil}},
which has the singleton type \colorbox{yellow}{\lstinline|nil|} in Typed Clojure.
This means, unlike Java's static type system, \emph{null} and reference types are separated as static types.
The programmer can then annotate Java methods and fields, specifying where \emph{null} is allowed.

@@

Typed Clojure types can express the most common usages of Clojure's sequence abstraction, 
which is a set of functions providing a common interface to collections.
These functions include:

\begin{itemize}
\item \colorbox{codebg}{\lstinline|seq|}, which takes a collection (or \colorbox{codebg}{\lstinline|nil|}) and returns
   \begin{itemize}
      \item a true value if the argument is non-empty
      \item a false value if the argument is empty (or \colorbox{codebg}{\lstinline|nil|})
   \end{itemize}
\item \colorbox{codebg}{\lstinline|first|}, which takes a collection (or \colorbox{codebg}{\lstinline|nil|}) and returns
   \begin{itemize}
      \item the first item of the argument if the argument is non-empty
      \item \colorbox{codebg}{\lstinline|nil|} if the argument is empty (or \colorbox{codebg}{\lstinline|nil|})
    \end{itemize}
\end{itemize}

@@

Heterogeneous map types that record the \emph{presence} of keyword keys
are sufficient to type check the most common usages of the Clojure idiom of using plain maps with known keyword keys.

\begin{description}
  \item[Map Literals] \colorbox{codebg}{\lstinline|\{:a 1 :b 2\}|} creates a map value with two entries, and
        is of the heterogeneous map type \colorbox{yellow}{\lstinline{'\{:a Number :b Number\}}}
  \item[Associating keyword keys] \colorbox{codebg}{\lstinline|(assoc \{:a 1 :b 2\} :c 3)|} 
      extends the first argument with a new entry with key \lstinline|:c|, and
        is of type \colorbox{yellow}{\lstinline{'\{:a Number :b Number :c Number\}}}
  \item[Dissociating keyword keys] \colorbox{codebg}{\lstinline|(dissoc \{:a 1 :b 2\} :a)|} dissociates 
      from the first argument the entry with key \lstinline|:a|, and
        is of type \colorbox{yellow}{\lstinline|'\{:b Number\}|}
  \item[Keyword lookup] \colorbox{codebg}{\lstinline|(get \{:a 1 :b 2\} :a)|} 
      returns the value corresponding to the key \lstinline|:a| in the first argument, and
        is of type \colorbox{yellow}{\lstinline|Number|}
\end{description}

@@

A function relying heavily on Java interoperability was ported successfully.
This function chained several Java calls together, and
Typed Clojure was able to express and check invariants related to occurrences of \emph{null}
and primitive arrays.

@@

There is significant future work.

@@

\begin{posterbox}[name=references,column=2,below=conclusion]{References}
  \smaller
  \bibliographystyle{ieee}
  \renewcommand{\section}[2]{\vskip 0.05em}
  \begin{thebibliography}{1}\itemsep=-0.01em
    \setlength{\baselineskip}{0.4em}
    \bibitem{tob10:bnb}
    Tobin-Hochstadt, S.
    \newblock {T}yped {S}cheme: {F}rom {S}cripts to {P}rograms
    \newblock PhD Dissertation,
    \newblock Northeastern University, 2010
  \end{thebibliography}
  \vspace{0.3em}
